%-------------------------
% Sunil Rathod — ATS-Optimised One-Page Resume
% Compiled with pdflatex
%-------------------------
\documentclass[letterpaper,10pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{microtype}

% Page margins
\usepackage[top=0.35in, bottom=0.35in, left=0.45in, right=0.45in]{geometry}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust section spacing
\titleformat{\section}{\vspace{-7pt}\scshape\raggedright\large}{}{0em}{}[\titlerule\vspace{-4pt}]

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubheading}[4]{
  \item
    \textbf{#1} \hfill \small#2 \\
    \textit{\small#3} \hfill \textit{\small #4}
}
\newcommand{\resumeProjectHeading}[2]{
  \item \textbf{#1} \hfill \small{#2}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=12pt, itemsep=-2pt, parsep=0pt, topsep=1pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}

\setlength{\footskip}{4.08003pt}

%-------------------------------------------
\begin{document}

%---------- HEADER ----------
\begin{center}
  {\LARGE \textbf{Sunil Rathod}} \\[3pt]
  \small
  shrathod515@gmail.com \ $|$ \
  +91 82006 85503 \ $|$ \
  Ahmedabad, Gujarat, India \ $|$ \
  \href{https://linkedin.com/in/sunilrathod27}{linkedin.com/in/sunilrathod27}
\end{center}

%---------- PROFESSIONAL SUMMARY ----------
\section{Summary}
Full Stack Developer with 4+ years of experience building real-time industrial IoT dashboards, enterprise ERP integrations, and cloud-native web platforms using Vue.js, Nuxt 3, and Node.js. Currently leading frontend development of a Digital Asset Management (DAM) platform. Certified in Gen AI (Outskill, 2025) with hands-on expertise in LLM integration, AI agents, and vibe coding workflows (Cursor, Claude, ChatGPT, Gemini). Proven ability to deliver end-to-end features from architecture to deployment on AWS.

%---------- TECHNICAL SKILLS ----------
\section{Technical Skills}
\small
\textbf{Frontend:} Vue.js 3, Nuxt 2 \& 3, Vuetify, Pinia, Composition API, TypeScript, Tailwind CSS, Chart.js \\
\textbf{Backend:} Node.js, Express.js, REST APIs, WebSockets, MQTT, Cron Jobs \\
\textbf{Database:} MySQL, PostgreSQL, MongoDB, Typesense \\
\textbf{Cloud \& DevOps:} AWS (EC2, S3, CloudFront), Docker, PM2, GitLab CI/CD, Git \\
\textbf{Integrations:} QAD ERP (XML + REST), WhatsApp API, Twilio SMS, AWS SNS \\
\textbf{Gen AI \& LLMs:} OpenAI API, Prompt Engineering, AI Agents, Voice Agents, RAG, LLM Integration \\
\textbf{AI / Vibe Coding:} Cursor IDE, Claude AI, ChatGPT, Google Gemini, Bolt.new \\
\textbf{Specialisations:} IoT \& MQTT, Real-Time Dashboards, Digital Asset Management, ERP Automation

%---------- WORK EXPERIENCE ----------
\section{Work Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Frontend Lead — Collage DAM Platform}{Apr 2024 -- Present}
    {Rivulet Digital IQ}{Remote, India}
  \resumeItemListStart
    \resumeItem{Architected and built a full-featured Digital Asset Management platform handling enterprise-scale media libraries with millions of assets using Vue.js 3 and Node.js.}
    \resumeItem{Engineered AWS S3 asset pipeline supporting drag-and-drop uploads, folder/collection organisation, and bulk file move/copy/duplicate operations.}
    \resumeItem{Implemented Typesense full-text search, cutting media retrieval time significantly across multi-million asset libraries.}
    \resumeItem{Designed dynamic metadata management, custom fields, user/role management with subscription plans, and a public/private Brand Portal.}
    \resumeItem{Integrated AI coding tools (Cursor, Claude AI) into the development workflow, accelerating feature delivery by approximately 40\%.}
  \resumeItemListEnd

  \resumeSubheading
    {Senior Full Stack Developer}{Jun 2022 -- May 2024}
    {Aliter Business Solutions Pvt. Ltd.}{Ahmedabad, Gujarat}
  \resumeItemListStart
    \resumeItem{Led Evolve Automation v3: migrated QAD ERP integration from legacy XML to REST APIs with a redesigned Nuxt 3 frontend, reducing integration complexity for manufacturing clients.}
    \resumeItem{Built MT Auto Craft IoT v3 factory intelligence dashboard with real-time machine tracking, employee tool usage, and ERP sync via WebSockets and MQTT.}
    \resumeItem{Delivered PharmEasy IoT cold chain dashboard with configurable temperature breach alerts (WhatsApp, Email, SMS), ensuring pharmaceutical cold-chain compliance.}
    \resumeItem{Conducted on-site factory visits to identify operational gaps and translate floor-level requirements into production-ready software.}
  \resumeItemListEnd

  \resumeSubheading
    {Graduate Trainee $\to$ Web Developer}{Sep 2021 -- May 2022}
    {Aliter Business Solutions Pvt. Ltd.}{Ahmedabad, Gujarat}
  \resumeItemListStart
    \resumeItem{Developed Evolve Automation v2 (Nuxt 3 + Node.js + QAD ERP XML), streamlining factory production data workflows across multiple clients.}
    \resumeItem{Built MT Auto Craft IoT v2 MQTT dashboard for real-time machine output monitoring and cold storage alerting via SMS, WhatsApp, and Email.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%---------- KEY PROJECTS ----------
\section{Key Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {Collage — Digital Asset Management Platform}{Vue.js · Node.js · AWS S3 · Typesense}
  \resumeItemListStart
    \resumeItem{Enterprise DAM with asset management, advanced search, metadata system, brand portals, and analytics dashboard for large-scale digital media operations.}
  \resumeItemListEnd

  \resumeProjectHeading
    {MT Auto Craft IoT v3 — Factory Intelligence Dashboard}{IoT · MQTT · Nuxt 3 · WebSockets · QAD ERP}
  \resumeItemListStart
    \resumeItem{Real-time factory floor dashboard with machine tracking, employee tool usage monitoring, and ERP data sync.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%---------- EDUCATION ----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Bachelor of Computer Applications (BCA)}{2018 -- 2021}
    {Gujarat University}{Ahmedabad, Gujarat}
\resumeSubHeadingListEnd

%---------- CERTIFICATIONS ----------
\section{Certifications}
\resumeItemListStart
  \resumeItem{\textbf{Gen AI Accelerator Program} — Outskill (2025) | LLMs, OpenAI API, Prompt Engineering, AI Agents, Voice Agents, RAG, AI Monetization}
  \resumeItem{The Fundamentals of Digital Marketing — Google}
  \resumeItem{Machine Learning with Python – Level 1 — IBM \quad | \quad Python 101 for Data Science — IBM}
  \resumeItem{Python (Basic) — HackerRank}
\resumeItemListEnd

\end{document}
